% KERdoc.tex V1.0, 14 June 2004

\documentclass{KERauth}
%\usepackage{times}

\begin{document}
\KER{1}{24}{00}{0}{2004}{S000000000000000}

\runningheads{A. Smith}{A demonstration of The Knowledge
Engineering Review class file}

%\doublespacing

\title{A Blockchain based Decentralised Booking System}

\author{Naipeng Dong$^1$, Guangdong Bai$^2$, Lung-Chen Huang$^1$, Kok Heng Lim$^1$ and Jin Song Dong$^{1,2}$}
\address{$^1$SoC, National University of Singapore, ~$^2$Griffith University\\
\email{dcsdn@nus.edu.sg}}


\begin{abstract}
This 
\end{abstract}

\section{Introduction}
The blockchain technology has rapidly emerged in recent years, especially when the concept of smart contract
was rst introduced to and later relied on the technology. Once The smart contract code is deployed to the
blockchain, it can be executed by any computer node that keeps the same historical record of transactions as
other nodes. This makes it diffcult to be compromised with a single node on the network, unlike centralized
platforms that could be easily breached and prone to the failure of single point. However, decentralized
platforms are still in its infancy. Although some communities and companies have proposed some use cases
for the logistics and insurance industry, its use cases are lacking in different domains. To give a more concrete
example of using the smart contract, we model a fundamental architecture of a decentralized hotel booking
system with PAT CSP\# in [1], and explore the potential of the system design with assertions of system
properties in the report.

Most travelers would have hard times nding a hotel room for their next journey. They would possibly
browse through pages of entries on online travel agencies (OTAs) such as Booking.com or Agoda.com. As
we can imagine, it is time-consuming that each time a search result appears on the screen, they have to
delve into the deals one by one, which could be overlapping in the last search results. In order to alleviate
this monotonous experience, we shall leverage the blockchain technology and allow our search requests to
be deployed as smart contracts such that the process of discovery is left to the decentralized system, where
hoteliers can easily match their rooms with the criteria required by a traveler.

Our approach is to provide users with an interface where they can draft their booking request with the
requirement of a hotel room in a domain-specic language, which is similar to a real contract in a human-
readable form. Thereafter, the interface compiles the request into a machine-readable form and injects some
predened functions. Later, the user can deploy the request onto the blockchain. Once the request is visible
to other nodes, hoteliers can propose offers by invoking a function in the request. When the user is notied
of new proposals, the interface automatically starts a selection process of the proposals depending on the
request criteria from the user, showing the matched results. At the end, the user and one of the hoteliers seal
a deal.

\section{System design}
To more clearly illustrate the workings of our system, the system sequence diagram below describes
how travelers and hoteliers interact on the decentralized booking platform.

\section{System modelling}
User A user could be a traveler or hotelier who sends a transaction by invoking a function that includes
the address of the user, function name, gas, and gas price. A traveler can invoke Fetch to acquire the latest
set of proposals submitted by hoteliers, or to Settle for a specic proposal. A hotelier can invoke Propose
to send their proposals to the request.
Miner Each miner has its own transaction pool TxPool that continuously receives a new transaction with
gas greater than zero. Moreover, TxBlock to be executed by a miner also nds the new transactions with
more than or equal to a specied transaction gasPrice from the pool.
Request A request deployed by a traveler to the blockchain is a smart contract that accepts proposals
and can be invoked by the users.


\end{document}